curatedMetagenomicData

### 2019-10-04 curatedMetagenomic_NS.Rmd
updated

# Remove   everything without a country
pseq.subset <- subset_samples(pseq, !is.na(mnd))

# Pick the core (>0.1% relative abundance in >50% of the samples)
pseq.csubset <- core(pseq.subset, detection = 0.1/100, prevalence = 50/100)

wt = UniFrac(pseq.csubset, weighted=TRUE, normalized=FALSE, 
             parallel=FALSE, fast=TRUE)
plot(hclust(wt), main="Weighted UniFrac distances")

any(taxa_sums(pseq.csubset) == 0)

fpseq.core <- subset_taxa( pseq.core, !is.na(Phylum))

@@

tab <- diversities(pseq.csubset, index = "all")
stargazer(tab, type = "text",summary = NULL)
kable(head(tab))
plot(tab)
dev.off()

>>>>

# Remove   everything without a country
pseq.subset <- subset_samples(pseq, !is.na(mnd))
pseq.subset <- subset_samples(pseq, disease == "healthy")

keepotu = genefilter_sample(pseq, filterfun_sample(topp(0.05)), A=5)
f.pseq <- subset_taxa(pseq, keepotu)

any(taxa_sums(pseq.c) == 0)

genus.pseq <- subset_taxa( pseq.subset, !is.na(Genus))
phylum.pseq <- subset_taxa( pseq, is.na(Class) & !is.na(Phylum))

taxonomy <- tax_table(genus.pseq)
# Pick the core (>0.1% relative abundance in >50% of the samples)
pseq.subsetc <- core(pseq.subset, detection = 0.1/100, prevalence = 50/100)

map_levels(NULL, "Phylum","Genus",pseq.c)

diversities(phylum.pseq, index = "all")

png("alpha.png")

tab <- diversities(pseq.c, index = "all")
stargazer(tab, type = "text",summary = NULL)

tab <- diversities(pseq.subsetc, index = "Shannon")
tab <- diversities(phylum.pseq, index = "all")
stargazer(tab, type = "text",summary = NULL)
kable(head(tab))
plot(tab)
dev.off()

# Get metadata
pseq.meta <- meta(phylum.pseq)
kable(head(pseq.meta))
stargazer(pseq.meta, type = "text",summary = NULL)

# Add the diversity table to metadata
pseq.meta$Shannon <- tab$shannon 
pseq.meta$InverseSimpson <- tab$inverse_simpson
pseq.meta$fisher <- tab$fisher
pseq.meta$chao1 <- tab$chao1
#wt = UniFrac(pseq.csubset, weighted=TRUE, normalized=FALSE, 
#             parallel=FALSE, fast=TRUE)
#plot(hclust(wt), main="Weighted UniFrac distances")

library(ggpubr)

p1 <- ggviolin(pseq.meta, x = "mnd", y = "Shannon",
 add = "boxplot", fill = "mnd", palette = "paired") + theme(axis.text.x = element_text(angle = 90)) + theme(legend.position="none") + xlab("")
  print(p1)
ggsave("nation_violin_shannon.png")

@@

tab <- diversities(pseq.subset, index = "all")
stargazer(tab, type = "text",summary = NULL)
kable(head(tab))
plot(tab)
dev.off()
